Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
notes to self for redesign section

{\color {red}

Only use the following if it helps explain some things. Make sure the tone of things are positive, and explain that making a good interface is harder than it seems.

>>>>

{\color {red} 
Talk about the problems from the previous results section, and how we plan to change them,
along with a heuristic evaluation of the interface.

Talk about the process of designing a new interface, and how we tested it with BLUES and the
Tor Developers.

Talk about the improvements in heuristics from the existing to the redesigned interface, along 
with hopes of what we want our empirical goals to be (to increase success rate and to minimize
time to completion, which we do by some proxy detection, giving specific directions, etc.).

...

Only use the following if it helps explain some things. Make sure the tone of things are positive, and explain that making a good interface is harder than it seems.\\
